---
title: "EDA"
author: "Julie Kim"
date: "2/13/2019"
output: html_document
---

    ```{r setup, include=FALSE}
    knitr::opts_chunk$set(echo = TRUE)
    ```
    
    ```{r, warning = FALSE, message = FALSE}
    library(tidyverse)
    library(ggplot2)
    library(glmnet)
    library(pander)
    library(randomForest)
    ```

#### Read In Data

    ```{r, message=F, warning=F}
    data.norm <- read.csv('Normalized_Cleaned_Full_Dataset.csv', header=T)
    data.change.norm <- read.csv('Normalized_Cleaned_Full_Dataset_ChangeScore.csv', header=T)
    data.ACT.norm <- read.csv('Normalized_Cleaned_Activity_Dataset.csv', header=T)
    data.CON.norm <- read.csv('Normalized_Cleaned_Connectivity_Dataset.csv', header=T)
    data.ATT.norm <- read.csv('Normalized_Cleaned_AttentionLevel_Dataset.csv', header=T)
    data.alpha.norm <- read.csv('Normalized_Cleaned_AlphaBand_Dataset.csv', header=T)
    data.theta.norm <- read.csv('Normalized_Cleaned_ThetaBand_Dataset.csv', header=T)
    ```
    
###Diagnostics

    PCA

```{r}
res.norm = prcomp(data.norm[,-c(1:2)], scale=TRUE, center=TRUE)
res.change.norm = princomp(data.change.norm[,-c(1:2)])
res.ACT.norm = princomp(data.ACT.norm[,-c(1:2)])
res.CON.norm = princomp(data.CON.norm[,-c(1:2)])
res.ATT.norm = prcomp(data.ATT.norm[,-c(1:2)], scale=TRUE, center=TRUE)
res.alpha.norm = princomp(data.alpha.norm[,-c(1:2)])
res.theta.norm = princomp(data.theta.norm[,-c(1:2)])
plot(res.norm$x[,1],res.norm$x[,2],
     col=c("red","blue")[data.norm$ADHD+1], pch=16, asp=TRUE)
plot(res.change.norm$scores[,1],res.change.norm$scores[,2],
     col=c("red","blue")[data.change.norm$ADHD+1], pch=16, asp=TRUE)
plot(res.ACT.norm$scores[,1],res.ACT.norm$scores[,2],
     col=c("red","blue")[data.ACT.norm$ADHD+1], pch=16, asp=TRUE)
plot(res.CON.norm$scores[,1],res.CON.norm$scores[,2],
     col=c("red","blue")[data.CON.norm$ADHD+1], pch=16, asp=TRUE)
plot(res.ATT.norm$x[,1],res.ATT.norm$x[,2],
     col=c("red","blue")[data.ATT.norm$ADHD+1], pch=16, asp=TRUE)
plot(res.alpha.norm$scores[,1],res.alpha.norm$scores[,2],
     col=c("red","blue")[data.alpha.norm$ADHD+1], pch=16, asp=TRUE)
plot(res.theta.norm$scores[,1],res.theta.norm$scores[,2],
     col=c("red","blue")[data.theta.norm$ADHD+1], pch=16, asp=TRUE)
```


###Modeling
    
    Base Misclassification Rate - we use this is a comparison to the models. 
    "If we guessed that all subjects did not have ADHD, how would we perform /
    how often would we be incorrect?"
    Every model under consideration should perform *at least* better than this 
    base misclassification rate. If not, don't even bother!
    ```{r}
    br = function(data) {return(mean(data$ADHD == 0))}
    base = br(data.norm)
    br(data.change.norm)
    br(data.ACT.norm)
    br(data.CON.norm)
    br(data.ATT.norm)
    br(data.alpha.norm)
    br(data.theta.norm)
    ```
    
####Elastic Net (Lasso and Ridge Regression Combined)

    Model fitting &  Cross Validation (number of folds should be specified)
    ```{r}
    #Cross Validation and Test Error - specify the number of folds
    ###WANHE & JAE'S CODE HERE
    
    test_error <- function(data){
      #leave out 10% of test data and get the misclassification rate
      n <- nrow(data)
      m <- round(.1*n)
      test_er<- numeric(0)
      train_er <- numeric(0)
      for(i in 1:100){
        test_indx <- sample(1:n, m, replace=FALSE)
        test <- data[test_indx,]
        train <- data[-test_indx,]
        #cross validation
        cvfit <- cv.glmnet(y=train$ADHD, x=as.matrix(train[, -c(1,2)]), 
                           family="binomial", alpha=0.7, 
                           type.measure = "class", nfolds=5)
        test_er[i] <- mean(predict(cvfit, s="lambda.min", type="class", 
                                   newx = as.matrix(test[, -c(1,2)])) != test$ADHD)
        train_er[i] <- mean(predict(cvfit, s="lambda.min", type="class", 
                                    newx = as.matrix(train[, -c(1,2)])) != train$ADHD)
      
      }
      return(list(train_er, test_er))
    }
    ```
    ```{r, cache = TRUE, autodep = TRUE}
    set.seed(100)
    mis_rate_norm <- test_error(data.norm)
    mis_rate_change_norm <- test_error(data.change.norm)
    mis_rate_act_norm <- test_error(data.ACT.norm)
    mis_rate_con_norm <- test_error(data.CON.norm)
    mis_rate_att_norm <- test_error(data.ATT.norm)
    mis_rate_alpha_norm <- test_error(data.alpha.norm)
    mis_rate_theta_norm <- test_error(data.theta.norm)
    ```
    ```{r}
    set.seed(100)
    mean(mis_rate_norm[[1]])
    mean(mis_rate_norm[[2]])
    
    mean(mis_rate_change_norm[[1]])
    mean(mis_rate_change_norm[[2]])
    mean(mis_rate_act_norm[[1]])
    mean(mis_rate_act_norm[[2]])
    mean(mis_rate_con_norm[[1]])
    mean(mis_rate_con_norm[[2]])
    mean(mis_rate_att_norm[[1]])
    mean(mis_rate_att_norm[[2]])
    
    mean(mis_rate_alpha_norm[[1]])
    mean(mis_rate_alpha_norm[[2]])
    mean(mis_rate_theta_norm[[1]])
    mean(mis_rate_theta_norm[[2]])
    
    plot(c(1:7), c(mean(mis_rate_norm[[1]]), mean(mis_rate_change_norm[[1]]), 
                   mean(mis_rate_act_norm[[1]]), mean(mis_rate_con_norm[[1]]), 
                   mean(mis_rate_att_norm[[1]]), mean(mis_rate_alpha_norm[[1]]), 
                   mean(mis_rate_theta_norm[[1]])), ylim=c(0.1, 0.68), 
         ylab="misclassification error", type="l", xlab="dataset", col="blue")
    lines(c(1:7), c(mean(mis_rate_norm[[2]]), mean(mis_rate_change_norm[[2]]), 
                    mean(mis_rate_act_norm[[2]]), mean(mis_rate_con_norm[[2]]), 
                    mean(mis_rate_att_norm[[2]]), mean(mis_rate_alpha_norm[[2]]),
                    mean(mis_rate_theta_norm[[2]])), col="red")
    legend("topright",legend = c("test error", "train error"), 
           col = c("red", "blue"), lty=1, cex=0.8)
    ```
    
    Diagnosis for second full dataset
    ```{r}
    cvfit <- cv.glmnet(y=data.change.norm$ADHD, 
                       x=as.matrix(data.change.norm[, -c(1,2)]), 
                       family="binomial", alpha=0.7, 
                       type.measure = "class", nfolds=5)
    coef(cvfit)
    ```
    
    Tuning alpha: Run through alpha values from 0 to 1 in increments of 0.1. 
    Return a table of alpha values and the number of times out of 500 trials 
    that it produces the minimum misclassification error. The alpha values that 
    minimize the misclassification error for the `data.change.norm` dataset 
    are 0.8 and 0.9. 
    ```{r, cache = TRUE, autodep = TRUE}
    set.seed(100)
    minimums = vector()
    for(i in 1:500) {
      ms = vector(length = 11)
      names(ms) = seq(0, 1, by = 0.1)
      for(a in seq(0, 1, by = 0.1)) {
      er.fit = glmnet(x = as.matrix(data.change.norm[,-c(1,2)]), 
                    y = data.change.norm$ADHD, family = "binomial", alpha = a)
      cv.fit = cv.glmnet(x = as.matrix(data.change.norm[,-c(1,2)]), 
                       y = data.change.norm$ADHD, family = "binomial", 
                       alpha = a, type.measure = "class", nfolds = 5)
      ms[a*10+1] = signif(cv.fit$cvm[which(cv.fit$lambda == cv.fit$lambda.min)], 2)
      }
      minimums = c(minimums, names(ms)[ms == min(ms)])
    }
    sort(table(as.numeric(minimums)))
    #returns best alpha
    #0 0.1 0.3 0.2 0.5 0.4 0.6 0.7   1 0.8 0.9
    #8  21  42  47  57  60  72  73  94  97  97
    ```
    
    Analysis with alpha = 0.9
    ```{r}
    set.seed(100)
    #Fit Elastic Net regression and choose significant classifiers/ predictors
    #Cross Validation - specify the number of folds
    er.fit = glmnet(x = as.matrix(data.change.norm[,-c(1,2)]), 
                    y = data.change.norm$ADHD, family = "binomial", alpha = 0.9)
    
    cv.fit = cv.glmnet(x = as.matrix(data.change.norm[,-c(1,2)]), 
                       y = data.change.norm$ADHD, family = "binomial", 
                       alpha = 0.9, type.measure = "class", nfolds = 5)
    
    #The optimal value of λ, by 5-fold cross-validation, is 0.075. 
    #The MSE with this penalty is 0.34.
    signif(cv.fit$lambda.min, 2)
    signif(cv.fit$cvm[which(cv.fit$lambda == cv.fit$lambda.min)], 2)
    
    #Plot of lambdas with vertical line at minimizing lambda
    plot.glmnet(er.fit, "lambda")
    abline(v = log(cv.fit$lambda.min), col = "dimgray")
    ```

    Graphic Analysis
    ```{r}
    set.seed(100)
    # Model Predictions vs. True Observations
    er.pred = predict(cv.fit, newx = as.matrix(data.change.norm[,-c(1,2)]), 
                      s = "lambda.min", type = "response")
    plot(data.change.norm$ADHD, er.pred, 
         main = "Model Predictions vs. True Observations",
         xlab = "Diagnosis", ylab = "Predictions")
    ```
    
    Bootstrapping
    ```{r}
    #Bootstrapping code revised based on code from ADAFAEPOV Chapter 6, Cosma Shalizi
    resample = function(x) {sample(x, size = length(x), replace = TRUE)}
        
    resample.data.frame = function(data) {
      sample.rows = resample(1:nrow(data))
      return(data[sample.rows, ])
    }
    
    rboot = function(statistic, simulator, B) {
      tboots = replicate(B, statistic(simulator()))
      if (is.null(dim(tboots))) {
        tboots = array(tboots, dim = c(1, B))
      }
      return(tboots)
    }
    
    bootstrap = function(tboots, summarizer, ...) {
      summaries = apply(tboots, 1, summarizer, ...)
      return(t(summaries))
    }
    
    bootstrap.se = function(statistic, simulator, B) {
      bootstrap(rboot(statistic, simulator, B), summarizer = sd)
    }
    
    equitails = function(x, alpha) {
      lower = quantile(x, alpha/2)
      upper = quantile(x, 1 - alpha/2)
      return(c(lower, upper))
    }
        
    bootstrap.ci = function(statistic = NULL, simulator = NULL, tboots = NULL, 
                            B = if (!is.null(tboots)) {ncol(tboots)}, 
                            t.hat, level) {
      
      if (is.null(tboots)) {
        stopifnot(!is.null(statistic))
        stopifnot(!is.null(simulator))
        stopifnot(!is.null(B))
        tboots = rboot(statistic, simulator, B)
      }
      
      alpha = 1 - level
      intervals = bootstrap(tboots, summarizer = equitails, alpha = alpha)
      upper = t.hat + (t.hat - intervals[, 1])
      lower = t.hat + (t.hat - intervals[, 2])
      CIs = cbind(lower = lower, upper = upper)
      
      return(CIs)
      
    }
    ```
    ```{r, include = FALSE, warning = FALSE, message = FALSE}
    #Function mc.cis()
    #Returns the a-level CI of an elastic-net model's misclassification rates
    #Method of Prediction: Case Resampling
    #Input
      #Data frame on stocks with dates and stock prices or returns (df)
      #Alpha level for confidence interval (a)
    #Output
      #Misclassification Error
    
    mc.cis = function(df, a = 0.95) {
      
      en.mdl = cv.glmnet(y = df$ADHD, x = as.matrix(df[,-c(1,2)]), 
                         family = "binomial", alpha = 0.9, 
                         type.measure = "class", nfolds = 5)
      mc = mean(predict(en.mdl, s = "lambda.min", type = "class", 
                        newx = as.matrix(df[,-c(1,2)])) != df$ADHD)
        
      resample = function() {resample.data.frame(df)}
          
      estimator = function(data) {
        en.mdl = cv.glmnet(y = data$ADHD, x = as.matrix(data[,-c(1,2)]), 
                           family = "binomial", alpha = 0.9, 
                           type.measure = "class", nfolds = 5)
        mc =  mean(predict(en.mdl, s = "lambda.min", type = "class", 
                        newx = as.matrix(data[,-c(1,2)])) != data$ADHD)
        return(mc)
      }
      
      mc.cis = bootstrap.ci(statistic = estimator,
                            simulator = resample, 
                            B = 1000, t.hat = mc, 
                            level = a)
      
      return(mc.cis)
      
    }
    ```
    ```{r, cache = TRUE, autodep = TRUE}
    set.seed(100)
    #Misclassification Rate - Confidence Intervals by Bootstrapping over 1000 iterations
    #95%
    mc.cis(data.change.norm)
    #90%
    mc.cis(data.change.norm, 0.9)
    ```

####Random Forest
    Model fitting &  Cross Validation (number of folds should be specified)
    ```{r}
    set.seed(100)
    #diagnosis for second full dataset
    rf.mdl = randomForest(x = as.matrix(data.change.norm[,-c(1,2)]),
                          y = data.change.norm$ADHD,
                          ntree = 600)
    plot(data.change.norm$ADHD, predict(rf.mdl), 
         main = "Model Predictions vs. True Observations",
         xlab = "Diagnosis", ylab = "Predictions")
    
    #Error vs. # of Trees
    plot(rf.mdl)
    
    #roughly 45% misclassification
    mean(ifelse(predict(rf.mdl) > 0.5, 1, 0) != data.change.norm$ADHD)
    
    pred = predict(rf.mdl)
    CM = table(pred, data.change.norm$ADHD)
    
    #MSE = 0.2423
    mean(rf.mdl$mse)
    
    #Variable Importance Plot
    varImpPlot(rf.mdl, sort = T, n.var = 10,
               main = "Top 10 - Variable Importance")
    ```
    ```{r, message = FALSE, warning = FALSE, cache = TRUE, autodep = TRUE}
    set.seed(100)
    mc.rf.pred = function(data, threshold = 0.5) {
      mdl = randomForest(x = as.matrix(data[,-c(1,2)]),
                         y = data$ADHD,
                         ntree = 600)
      pred = predict(mdl)
      
      #1. Return probability that class = 1
      #2. Threshold said probabilities to output 0 or 1; default is 0.5
      #ROC Curve can help define those threholds
        #grid from 0 to 1, increments of 0.1
        #try picking the right parameter the minimizes training error the most
      mc = numeric(0)
      for(i in seq(0, 1, by = 0.1)) {
        mc[i*10+1] = mean(ifelse(pred > i, 1, 0) != data$ADHD)
      }
      plot(seq(0, 1, by = 0.1), mc, type = "l", 
           main = deparse(substitute(data)), 
           xlab = "Threshold", ylab = "Misclassification Rate")
      return(mean(ifelse(pred > threshold, 1, 0) != data$ADHD))
    }
    
    mc.rf.pred(data.norm, 0.7)
    mc.rf.pred(data.change.norm, 0.5)
    mc.rf.pred(data.ACT.norm, 0.7)
    mc.rf.pred(data.CON.norm, 0.8)
    mc.rf.pred(data.ATT.norm, 0.7)
    mc.rf.pred(data.alpha.norm, 0.8)
    mc.rf.pred(data.theta.norm, 0.6)
    ```
    ```{r, message = FALSE, warning = FALSE, cache = TRUE, autodep = TRUE}
    mc.rf = function(data) {
      n <- nrow(data)
      m <- round(.1*n)
      error = numeric(0)
      
      for(i in 1:100){
        test_indx <- sample(1:n, m, replace=FALSE)
        test <- data[test_indx,]
        train <- data[-test_indx,]
        #cross validation
        fit = randomForest(x = as.matrix(train[,-c(1,2)]), y = train$ADHD, 
                           ntree = 600)
        pred = ifelse(predict(fit, newdata = as.matrix(test[,-c(1,2)])) > 0.5, 1, 0)
        
        error[i] <- mean(pred != test$ADHD)
      }
      return(mean(error))
    }
    ```
    ```{r, message = FALSE, warning = FALSE, cache = TRUE, autodep = TRUE}
    set.seed(100)
    norm.mc.rf = mc.rf(data.norm)
    change.norm.mc.rf = mc.rf(data.change.norm)
    ACT.norm.mc.rf = mc.rf(data.ACT.norm)
    CON.norm.mc.rf = mc.rf(data.CON.norm)
    ATT.norm.mc.rf = mc.rf(data.ATT.norm)
    alpha.norm.mc.rf = mc.rf(data.alpha.norm)
    theta.norm.mc.rf = mc.rf(data.theta.norm)
    
    norm.mc.rf
    change.norm.mc.rf
    ACT.norm.mc.rf
    CON.norm.mc.rf
    ATT.norm.mc.rf
    alpha.norm.mc.rf
    theta.norm.mc.rf
    ```
    ```{r}
    #We observed a 36.47% increase in classification accuracy
    (base - 0.34)/base
    base
    ```


    Notes:
    + Sparse additive model is non-linear, and variables don't interact, generalization of linear regression with variable selection into the non-linear setting. Huge weakness: no way to design the functions such that the summation of the functions would give you a contour plot. Best for when data is sparse, i.e. p >> n.
    + Linear model is linear, all variables interact
    
    Cassie's notes after first analysis
    + Alpha and Theta analyses differently (which has highest accuracy rate)
    + Cassie has only looked @ Alpha (6-9 Hz), Theta is (3-7 Hz) and just included data for the sake of it
    + Attention Task instead of change scores (vs. baseline) - we should still keep change scores because there is a dependence between attention task and baseline
    + Non-normalized data
    + Visualization (topographic maps by James Long company): ERP Visualization
    + Training phase, is there any test data?
    + Q-Q Plot of residuals
    
####Logistic Regression

    Model fitting
    ```{r}
    #Fit logistic model
    data2 = data[,c(1,2,grep("ALPHA", colnames(data)))]
    lg.mdl = glm(ADHD ~ . -ID-ADHD, data = data2, family = binomial)
    plot(data$ADHD, predict(lg.mdl, type = "response"))
    predict(lg.mdl, type = "response")
    
    table(predict(lg.mdl, type = "response"), data$ADHD)
    
    #data.ATT
    #data.ATT.norm
    #data.change
    #data.change.norm
    ```
